EuPPollNet: A European database of plant-pollinator networks

### 2024-05-17 Manuscript/EuPPollNet_Ms.qmd
edits
Starting 3rd paragraph

@@

To assess the completeness of plant and pollinator species in the EuPPollNet database at European level, we used the aforementioned checklists for plants and pollinators. Specifically for plants, we refined the checklist to include only European flowering plants and excluded taxonomic groups not associated with biotic pollination. We did this by first excluding the families considered to have exclusively a wind pollination mode [see @culley2002], and then by filtering out the genera with wind or non-biotic pollination from families that exhibit both biotic and non-biotic pollination modes. Additionally, we manually included some exotic species and added unresolved species names that were not present in the accepted names of the checklist at the current version of usage. For pollinators, we compared only the taxonomic coverage of bees, syrphids and butterflies by using their species checklists at European level. Finally, to evaluate if the presence-absence of interaction records for bees and flowering plants follows a phylogenetic pattern within the database, we calculated its phylogenetic signal  at genus and family level, respectively. The phylogenetic signal was calculated by using the _phylosig_ function from the **phytools** package [@revell2012]. We extracted the phylogenetic information for bees from a genus level phylogeny [@hedtke2013] and processed it with the help of the packages **ape** [@paradis2019], **MCMCglmm** [@hadfield2010] and **phytools**; and for plants the phylogenetic tree was obtained from a species level PLANT phylogeny [@smith2018] with the help of **rtree** package [@li2023].

@@

**Network paragraph**

This higher number of pollinator species compared to plants seems to be a common feature of phytocentric sampled plant-pollinator networks [@jordano2016].

Link with interactions

Connectance
Nestedness
Pattern across latitude

@@

**Conclusion paragraph**
Geographic and taxonomic biases!
Supporting reference:
https://doi.org/10.1111/ecog.05926

>>>>

#Calculate mean coverage and deviation
coverage = c(bee_coverage, syrphid_coverage, lepidoptera_coverage)
mean_coverage = mean(coverage)
sd_coverage = sd(coverage)

@@

To assess the completeness of plant and pollinator species in the EuPPollNet database at European level, we used the aforementioned checklists for plants and pollinators. Specifically for plants, we refined the checklist to include only European flowering plants and excluded taxonomic groups not associated with biotic pollination. We did this by first excluding the families considered to have exclusively a wind pollination mode [see @culley2002], and then by filtering out the genera with wind or non-biotic pollination from families that exhibit both biotic and non-biotic pollination modes. Additionally, we manually included some exotic species and added unresolved species names that were not present in the accepted names of the checklist at the current version of usage. For pollinators, we compared only the taxonomic coverage of bees, syrphids and butterflies by using their species checklists at European level. The potential number of pollinator species at European level was estimated by adding the total number of species of bees, syrphids, and flies from the checklists, along with the extrapolated number of species from other insect pollinators. This extrapolated number was estimated by assuming that the sampling coverage of these other insect pollinators is equal to the average coverage across bees, syrphids, and butterflies (mean coverage = `r round(mean_coverage, 2)`; sd = `r round(sd_coverage,2)`).

Finally, to evaluate if the presence-absence of interaction records for bees and flowering plants follows a phylogenetic pattern within the database, we calculated its phylogenetic signal  at genus and family level, respectively. The phylogenetic signal was calculated by using the _phylosig_ function from the **phytools** package [@revell2012]. We extracted the phylogenetic information for bees from a genus level phylogeny [@hedtke2013] and processed it with the help of the packages **ape** [@paradis2019], **MCMCglmm** [@hadfield2010] and **phytools**; and for plants the phylogenetic tree was obtained from a species level plant phylogeny [@smith2018] with the help of **rtree** package [@li2023].

@@

Although Europe contains a much larger number of flowering plants than pollinator species (~4 to 1 ratio), the observed number of pollinator species almost doubled the one of observed plant species. This seems a common feature of phytocentric plant-pollinator networks, which tend to overlook rare plant species and capture a higher proportion of pollinator species [REF].

Discuss this

The number of pollinator species almost doubled the number of plant species within the database. This is a common aspect in phytocentric networks [@jordano2016], where an observer records the different pollinators that land on the reproductive structures of plants, resulting in a higher number of pollinator species per plant.

Link with connectance now?

Discuss that other type of informative networks could be useful an increase connectance?

visitation networks

Link with interactions -->

More species less connectance, which increases the number of missing links.

Nestedness
Pattern across latitude

Missing links?

networks condense information but this workflow allo possibility to explore species phenology... and more

@@

**Conclusion paragraph**

foundation for future work

Geographic and taxonomic biases!
Supporting reference:
https://doi.org/10.1111/ecog.05926
